---
title: "Notes for the Ofav-Acer response to Nutrients and CO2"
author: "Ana Palacio"
date: "September 8, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## QUESTIONS

 1. How do nutrient enrichment and CO2 affect: 
- Symbiont communities estructure and function (S:H, densities, Chl, Fv/Fm)
- Host function: Calcificaton and Lipids 
 in O.fav and A.cer

2.  How these species*treatments respond to thermal stress? (Bleaching response)
 - Symbiont communities estructure and function (S:H, densities, Chl, Fv/Fm),
 - Host function: Calcificaton, and Lipids
 
-----------------------------------------------

##  Planed data and sample collection 
 1. Nutrient concentrations 
 2. Temperature (HOBOs)
 4. Coral Biopsies
 5. Bouyant weight before and after sampling
 6. Cores + Blasting (Chl, cell counts and lipids)
 3. IPAM 

-----------------------------------------------

## Cores History
 1. Collection
 2. Coring
 3. Recovery
 
### Colonies 1-2-3-5
Most of these cores died after temp control broke twice. None has enough left to use in the experiment.

### Colony 4
This colony was big and we got a bunch of thermal resistant cores. Some of them recovered and could be used in the experiment. tAke into account they were already stressed. 
 
### Colony 6
 
Colony 6 (Volcano) has huge mortality in 9/8/16. Mortality in this same genotype started two weeks ago in cores in the wet lab and was spread to Ofav 7. CD was at the hatchery on 9/7/16 morning and did not notice anything. ~ 40 cores + some pieces were lost in ~ 40 hours. Partially dead cores were moved to another tank. 

### 2017
Almost all the cores died from the weird tissue lost. During march 2017 while I was in Galapagos the lab collected more colonies and some of those have been cored and are recovering. Two drill bite sizes were used since Ssid is not recovering very well with the smaller size. 


### Orbicella faveolata
### Colony 6: 
Only colony that has enogh cores left grom 2016. 48 cores, small size, with epoxy around
### Colony 9: 
Tag 702, got 61 cores, small size. Whole colony cored by AP and CD on 4/5/2017.
### Colony 10: 
No Tag ??, colony with multiple pieces since it was collected. Got 63 cores, small size and prtty green polyps. There are more from this colony to be cored.
### Colony 11: 
No Tag ??, Got 84 cores, whole colony cored, small cores.
### Colony 22: 
Tag 946, whole colony cored, small size. Finished by AP and CD on 4/01/2017.


### Siderastrea siderea
### Colony 20: 
Tag 950, got 106 core small size. Whole colony cored by AP and RC. ~20 cores from initial coring look very bad. 
### Colony 22: 
Tag 948, 66 big cores. Whole colony cored by AP, CD and PR. All the cores look ok
### Colony 23: 
Tag 941, 81 small cores. Whole colony cored.
### Colony 27: 
Tag 941, 98 small cores. Whole colony cored.
### Colony 30: 
Tag 713, 65 big cores. Whole colony cored by AP, CD and PR. All the cores look ok.

Samples for initial symbiont identification. 4/11/2017

* Ofav 6-86
* Ofav 6-96
* Ofav 6-107

* Ofav 9-50
* Ofav 9-20
* Ofav 9-24

* Ofav 10-59
* Ofav 10-A
* Ofav 10-B

* Ofav 11-A
* Ofav 11-B
* Ofav 11-C

* Ofav 22-36
* Ofav 22-12
* Ofav 22-27

* Ssid 20-91
* Ssid 20-49
* Ssid 20-36

* Ssid 22-A
* Ssid 22-B
* Ssid 22-C

* Ssid 23-A
* Ssid 23-B
* Ssid 23-C

* Ssid 27-36
* Ssid 27-13
* Ssid 27-88

* Ssid 30-A
* Ssid 30-B
* Ssid 30-C




 
## Problems to solve before start the experiment

1. How much nutrients need to be added to keep concentrations constant?


-----------------------------------------------
## DATA ANALISIS

### Data Cleaning

- Reformating and subsampling 
- Be sure that processed data is easy to follow from raw data
- Exploratory figures
- Check the data quality for the question 
- Statistical prediction modeling
- Final figures to pubish results 

Insert code like this 

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
