---
title: "Notes for the Ofav-Acer response to Nutrients and CO2"
author: "Ana Palacio"
date: "September 8, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## QUESTIONS

 1. How do nutrient enrichment and CO2 affect: 
- Symbiont communities estructure and function (S:H, densities, Chl, Fv/Fm)
- Host function: Calcificaton and Lipids 
 in O.fav and A.cer

2.  How these species*treatments respond to thermal stress? (Bleaching response)
 - Symbiont communities estructure and function (S:H, densities, Chl, Fv/Fm),
 - Host function: Calcificaton, and Lipids
 
-----------------------------------------------

##  Planed data and sample collection 
 1. Nutrient concentrations 
 2. Temperature (HOBOs)
 4. Coral Biopsies
 5. Bouyant weight before and after sampling
 6. Cores + Blasting (Chl, cell counts and lipids)
 3. IPAM 

-----------------------------------------------

## Cores History
 1. Collection
 2. Coring
 3. Recovery
 
### Colonies 1-2-3-5
Most of these cores died after temp control broke twice. None has enough left to use in the experiment.

### Colony 4
This colony was big and we got a bunch of thermal resistant cores. Some of them recovered and could be used in the experiment. tAke into account they were already stressed. 
 
### Colony 6
 
Colony 6 (Volcano) has huge mortality in 9/8/16. Mortality in this same genotype started two weeks ago in cores in the wet lab and was spread to Ofav 7. CD was at the hatchery on 9/7/16 morning and did not notice anything. ~ 40 cores + some pieces were lost in ~ 40 hours. Partially dead cores were moved to another tank. 
 
## Problems to solve before start the experiment

1. How much nutrients need to be added to keep concentrations constant?


-----------------------------------------------
## DATA ANALISIS

### Data Cleaning

- Reformating and subsampling 
- Be sure that processed data is easy to follow from raw data
- Exploratory figures
- Check the data quality for the question 
- Statistical prediction modeling
- Final figures to pubish results 

Insert code like this 

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
