---
title: "Notes about Data science specialization"
author: "Ana Palacio"
date: "September 8, 2016"
output: html_document
---
------------------------------------
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Titles are delimited with the equals 

# Specialization

0. Scientist toolbox
1. R programing
2. Getting data
3. Exploratory data analysis 
  - Exploatory graphs
  - Plotting systems in r
  - Multivariate data
  - Multiple modes of evidence
  
4. Reproducible research
5. Statistical inference: Generalizable information from data 
6. Regression models
7. Practical Machine learning
8. Building data products
  - R packages as devtools
  - rCharts
  - Shine 

------------------------------------------

0. SCIENTIST TOOLBOX
====================

# 2. Stats
# 3. Substantive expertise
# 1. Hacking skills: computing/coding (in this case in R) and being able to answer questions by yourself
--------------------------------------------------

## Getting help

### get help in R
  
  -?funcion
  - help.seach(function)
  - args("function")
  - function ... r givies you the syntaxix

### Ask for help 

When you ask for help: Give specific steps to reproduce the problem, versions, operation system, goal or expected results, actual result, what solutions are you thought about?

### Finding Answers

None of the knowlege you need will be in a notebook. It is skatter around. Try to: 

- Find where to look (Stackoverflow, use tag "[r]")
- Be Unitimidated by new data and packages
- Be unafraid to sayyou do not knwow the answers


## Comand line interface

  - Navegate folders, creat folders and files, edit...
  - Navegates in a directories that have a structure
  - Use command + Flags (preceded by -) + Arguments
      
      I.e. touch creates an empty file, mkdir creates a folder, pwd, clear, ls. cd, cp, rm, ....
  
## GIT and version control system. Same linux developers!

- Records changes to a file or set of files. Save o manage intermidiate files, important to colaborate. 

### Install git in your computer and configurate your account

user and email 

### Colaborae using GitHub using push and pull bw web and your local computer

- use same email adress that you use to conf git
- Create a repo: 

1. Start from scratch: 
 -
 
2. Fork from another user
  


----------------------------------------------

4. REPRODUCIBLE RESEARCH NOTES 
===========================

# Literate Statistical Programing

Literate programing lenguaje:  

- Sweve uses Latex, Latex if for weirdos  
- Markdown and Knit could use multiple and are integrated in Rstudio! 

## Basic Markdown syntaxis 

Above is a 2nd level header. Down there is a 3rd level header 

### Including code

Down is how you insert r code. In this case the code itself will be printed

```{r}
summary(cars)
```

If you use echo=F, only the result is printed. You can also name your piece of code, in this case = cars

```{r cars, echo=FALSE}
summary(cars)
```

### Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



## Caching computations
We use cacher packege in R to not recompute everything if there is not changes in the code, so getting the output document is faster. It lazy-load precomputaded results. Source code and metadata is downloades but not 

